---
title: "Compare Atlantis Scenario Output"
author: "Robert Wildermuth"
date: "1/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load atlantisom package and replacement functions
```{r}
library(atlantisom)
library(tidyverse)
library(tidync)
library(ggforce)
library(oce)

source("C:/Users/rwildermuth/Dropbox/PhD_UMass/ATLANTIS/omNEUS/load_neus_v1_runprm.R")
source("C:/Users/rwildermuth/Dropbox/PhD_UMass/ATLANTIS/omNEUS/run_truth.R")
```

Function to convert nitrogen into tonnes wet weight biomass for biomass pool inverts
```{r}
# Following Atlantis wiki (https://confluence.csiro.au/display/Atlantis/Atlantis+Output+Files)
# "* X_CN * mg_2_tonne where X_CN is the Redfield ratio specified in the biol.prm file (typically 5.7) and mg_2_tonne is 0.00000002"

ConvertBiomassPool <- function(groupSN, # structural nitrogen (mg) from Out.nc
                               X_CN = 5.7, # C:N Redfield ratio from biol.prm, called 'redfieldcn' in {atlantisom}
                               wetdry = 20, # wet to ash-free dry weight, 'k_wetdry' in biol.prm, same as 'kgw2d' in {atlantisom}
                               X_RS = 2.65 # Ratio of reserve to structural N in biol.prm
                               ){
  
  #Calculate wet weight of biomass pools using conversion in Atlantis manual, pg 151: weight_g = (1 + 2.65) * strutural N

  mgTotN <- groupSN * (1 + X_RS)

  # convert from mg N dry weight to mT wet weight biomass
  biomass <- mgTotN * wetdry * X_CN / 1e9
  return(biomass)
}

ConvertBiomassPool(groupSN = 10000)
```

Function to extract data
```{r}
# args: indBDNLookup, scenario, dir, file_fgs, file_bgm, select_groups, file_init, file_biolprm, 

# Pull in the data from Atlantis using modified run_truth()
truth <- run_truth(scenario = scenario,
                   dir = dir,
                   file_fgs = file_fgs,
                   file_bgm = file_bgm,
                   select_groups = select_groups,
                   file_init = file_init,
                   file_biolprm = file_biolprm,
                   file_runprm = "NEUSv1",
                   # saves to folder containing the Atlantis output
                   save = TRUE)

# Get the catches by species for Georges Bank
# Subset to Georges Bank boxes and apply biomass conversion
bio_catchGB <- calc_biomass_age(nums = truth$catch,
                                resn = truth$resn, structn = truth$structn, biolprm = truth$biol)
bio_catchGB <- bio_catchGB %>% filter(polygon %in% c(5, 7:11, 19)) %>%
                  # Divide box 5 values in half 
                  mutate(atoutput = case_when(polygon == 5 ~ atoutput/2,
                                              polygon != 5 ~ atoutput)) 
bio_catchGB <- aggregate(atoutput ~ species + time,
                         data = bio_catchGB, sum)


aggBioCatchGB <- merge(bio_catchGB, truth$bio_catch, by = c("species", "time"))
aggBioCatchGB$propGB <- with(aggBioCatchGB, atoutput.x/atoutput.y)

# multiply .txt catch by Georges Bank proportions and create pseudo-data time series
catchGB <- merge(truth$catch_all, aggBioCatchGB, by = c("species", "time"))
# remove initial year and unneeded columns
catchGB <- catchGB %>% filter(time != 0) %>%
              dplyr::select(species, time, atoutput, propGB) %>%
              mutate(catchGB = atoutput * propGB)


# Aggregate catch based on fish groups
commGF <- catchGB %>% 
              filter(species %in% indBDNLookup[indBDNLookup$BNindexGroup == "groundfish", "Name"]) %>%
              group_by(time) %>% 
              dplyr::summarize(commGF = sum(catchGB))
# ggplot() + geom_line(data = commGF, aes(x=time,y=commGF))

commPel <- catchGB %>% 
              filter(species %in% indBDNLookup[indBDNLookup$BNindexGroup == "forage", "Name"]) %>%
              group_by(time) %>% 
              dplyr::summarize(commPel = sum(catchGB))
# ggplot() + geom_line(data = commPel, aes(x=time,y=commPel))

# need to calculate catch of invertebrate groups similar to run_truth()
# 1. Pull catches for entire system
catchConnect <- tidync(file.path(dir, paste0(scenario, "TOTCATCH.nc")))
catchVars <- catchConnect %>% activate("D1,D0") %>% hyper_vars() # %>% select(name)
catchVars <- catchVars$name

search <- character()
for(i in indBDNLookup[indBDNLookup$BNindexGroup == "inverts", "Code"]){
# for(i in paste(indBDNLookup[indBDNLookup$BNindexGroup == "inverts", "Code"],
#                "Catch", sep = "_")){
  search <- c(search, grep(i, catchVars, fixed = TRUE, value = TRUE))
  }


# sfCatchNC <- catchConnect %>% activate(noquote("BFS_Catch_FC4")) %>% #activate(search[1]) %>%
#                 hyper_tibble()
sfCatchNC <- catchConnect %>% activate("D1,D0") %>% 
                hyper_tibble()

sfCatchNC <- sfCatchNC %>% select(b, t, numlayers, topk, all_of(search))

# Check that TOTCATCH.nc matches Catch.txt
# totCatchCheck <- sfCatchNC %>% group_by(t) %>%
#                     dplyr::summarize(Tot_BFS_Catch = sum(Tot_BFS_Catch),
#                                      Tot_BFS_RecCatch = sum(Tot_BFS_RecCatch),
#                                      Tot_BFS_Discards = sum(Tot_BFS_Discards),
#                                      Tot_BML_Catch = sum(Tot_BML_Catch),
#                                      Tot_BML_RecCatch = sum(Tot_BML_RecCatch),
#                                      Tot_BML_Discards = sum(Tot_BML_Discards))
# Values in "Catch" column similar to Catch.txt


# 2. pull out just the Georges Bank catches
commSF <- sfCatchNC %>% filter(b %in% c(5, 7:11, 19)) %>%
                  # Divide box 5 values in half 
                  mutate(Tot_BFS_Catch  = case_when(b == 5 ~ Tot_BFS_Catch /2,
                                                    b != 5 ~ Tot_BFS_Catch ), 
                         Tot_BML_Catch  = case_when(b == 5 ~ Tot_BML_Catch /2,
                                                    b != 5 ~ Tot_BML_Catch ),
                         Tot_PWN_Catch  = case_when(b == 5 ~ Tot_PWN_Catch /2,
                                                    b != 5 ~ Tot_PWN_Catch )) 

# 3. multiply CATCH.txt by the GB ratio
# Don't need to find 'biocatch' amounts, since can just pull relevant box total catch for groups of interest
# and can keep the given values as biomass of catch in tonnes

# 4. add species within inverts group together
commSF$commSF <- rowSums(commSF[ ,c("Tot_BFS_Catch", "Tot_BML_Catch", "Tot_PWN_Catch")])
commSF <- commSF %>% select(b, t, numlayers, topk, Tot_BFS_Catch, Tot_BML_Catch, Tot_PWN_Catch, commSF) %>%
              group_by(t) %>%
              dplyr::summarize(commSF = sum(commSF)) %>% 
              mutate(time = ((t/(60*60*24))-1)/365) #%>%
              #filter(time != 0) %>%
              #filter(time <= 50)


# ggplot() + geom_line(data = commSF, aes(x=t,y=commSF))

#Find biomasses for age-structured fish groups
# First convert to biomass (mT)
biomassTruth <- calc_biomass_age(nums = truth$nums,
                                 resn = truth$resn, structn = truth$structn, biolprm = truth$biol)

groundGB <- biomassTruth %>% 
              filter(species %in% indBDNLookup[indBDNLookup$BNindexGroup == "groundfish", "Name"]) %>%
              filter(polygon %in% c(5, 7:11, 19)) %>%
              group_by(time) %>% 
              dplyr::summarize(ground = sum(atoutput))
ggplot() + geom_line(data = groundGB, aes(x=time,y=ground))

forageGB <- biomassTruth %>% 
              filter(species %in% indBDNLookup[indBDNLookup$BNindexGroup == "forage", "Name"]) %>%
              filter(polygon %in% c(5, 7:11, 19)) %>%
              group_by(time) %>% 
              dplyr::summarize(forage = sum(atoutput))
ggplot() + geom_line(data = forageGB, aes(x=time,y=forage))

fgs <- load_fgs(dir = dir, file_fgs = file_fgs)
bps <- load_bps(dir = dir, fgs = file_fgs, file_init = file_init)
allboxes <- load_box(dir = dir, file_bgm = file_bgm)
bboxes <- get_boundary(allboxes)
invertsGB <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                     bps = bps, fgs = fgs, 
                     select_groups = indBDNLookup[indBDNLookup$BNindexGroup == "inverts", "Name"],
                     select_variable = "N", bboxes = bboxes)
invertsGB <- invertsGB %>% filter(polygon %in% c(5, 7:11, 19))

# Have to translate into biomass
invertsGB <- invertsGB %>% mutate(inverts = ConvertBiomassPool(groupSN = atoutput))

invertsGB <- invertsGB %>% group_by(time) %>% 
          dplyr::summarize(inverts = sum(inverts))
# ggplot() + geom_line(data = invertsGB, aes(x=time,y=inverts))

# ----------- Habitats -----------------

# use condition factor as indices for habitat calculations
condition <- merge(truth$resn, truth$structn, by = c("species", "agecl", "polygon", "layer", "time"))
condition$condition <- condition$atoutput.x/condition$atoutput.y

test6 <- condition %>% filter(condition < 2.65)
test6 <- condition %>% filter(condition > 2.65)
unique(unique(test6[,-c(6:8)])[, c("species", "agecl")])
dim(condition); dim(test6)
# need to select by mature age classes
matOgive <- truth$biolprm$maturityogive
matOgive <- merge(matOgive, fxnlGroups[, c("Code", "Name")], by.x = "code", by.y = "Code")
names(matOgive)[which(names(matOgive) == " agecl10")] <- "agecl10"
matOgive <- matOgive %>% dplyr::select("Name", paste0("agecl", 1:10)) %>%
              pivot_longer(cols = starts_with("agecl"), names_to = "agecl",
                           names_prefix = "agecl", names_ptypes = numeric(),
                           values_to = "propMat_fctr") %>%
              mutate(agecl = as.numeric(agecl),
                     propMat = as.numeric(as.character(propMat_fctr)))

#Calculate habitat as the number of mature indivs * their condition ratio
numMat <- merge(truth$nums, matOgive, by.x = c("species", "agecl"), by.y = c("Name", "agecl"))
numMat <- numMat %>% dplyr::select(species, agecl, polygon, layer, time, atoutput, propMat) %>%
            mutate(numMat = atoutput * propMat)
numMat <- merge(numMat, condition, by = c("species", "agecl", "polygon", "layer", "time"))

# need separate dataset for Nearshore Habitat
# doesn't work b/c no age groups -> no maturity ogive
numMatNear <- numMat %>% filter(species %in% c("Filter_Other",
                                               "Deposit_Feeder",
                                               "Meiobenth"))
  
numMat <- numMat %>% mutate(condIndex = numMat * condition)

numMat <- numMat %>% group_by(species, time) %>%
            dplyr::select(species, agecl, polygon, layer, time, condIndex) %>%
            dplyr::summarize(condIndex = sum(condIndex))

# ggplot() + 
#   geom_line(data=numMat, aes(x=time,y=condIndex), 
#             alpha = 10/10) +
#   facet_wrap(~species, ncol=3, nrow = 2, scales="free")

# aggregate by focal group similar to BDN
# Seafloor and Demersal Habitat
habDem <- numMat %>% filter(species %in% indBDNLookup[indBDNLookup$BNindexGroup == "groundfish",
                                                      "Name"])
habDem <- habDem %>% group_by(time) %>%
            dplyr::summarize(habDem = sum(condIndex)) 

plot(habDem$time, habDem$habDem, type = "l")

# Pelagic Habitat
habPel <- numMat %>% filter(species %in% indBDNLookup[indBDNLookup$BNindexGroup == "forage",
                                                      "Name"])
habPel <- habPel %>% group_by(time) %>%
            dplyr::summarize(habPel = sum(condIndex)) 
plot(habPel$time, habPel$habPel, type = "l")

# Nearshore Habitat
# do similar, but only for  lower trophic benthic groups for half of Box 5
habNear <-  numMatNear %>% filter(polygon == 5) %>%
              mutate(condIndex = numMat/2 * condition) %>% 
              group_by(species, time) %>%
              dplyr::select(species, agecl, polygon, layer, time, condIndex) %>%
              dplyr::summarize(condIndex = sum(condIndex))
habNear <- habNear %>% group_by(time) %>%
            dplyr::summarize(condIndex = sum(condIndex))
# plot(habNear$time, habNear$condIndex, type = "l")
```

Try to get biomass of bio pools for nearshore habitat
```{r}
bps <- load_bps(dir = dir, fgs = file_fgs, file_init = file_init)
fgs <- load_fgs(dir = dir, file_fgs = file_fgs)
invertPools <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                     bps = bps, fgs = fgs, 
                     select_groups = c("Filter_Other",
                                       "Deposit_Feeder",
                                       "Meiobenth"),
                     select_variable = "N", bboxes = bboxes)

test2 <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                        bps = bps, fgs = fgs, 
                        select_groups = c("Benthopel_Fish"),
                        select_variable = "N", bboxes = bboxes)
test3 <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                        bps = bps, fgs = fgs, 
                        select_groups = c("Benthopel_Fish"),
                        select_variable = "ResN", bboxes = bboxes)
test4 <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                        bps = bps, fgs = fgs, 
                        select_groups = c("Benthopel_Fish"),
                        select_variable = "StructN", bboxes = bboxes)
test2 %>% filter(polygon == 5, time == 0, layer == 0) # not the sum of structN and resN
test3 %>% filter(polygon == 5, time == 0, layer == 0)
test4 %>% filter(polygon == 5, time == 0, layer == 0)
```

Calculate wet weight of biomass pools using conversion in Atlantis manual, pg 151: weight_g = (1 + 2.65) * strutural N
```{r}
# Subset for Nearshore Habitat
truthNear <- invertPools %>% filter(polygon == 5, layer == 4) %>%
                mutate(habNear = ConvertBiomassPool(groupSN = atoutput))

truthNear <- truthNear %>% group_by(time) %>% 
          dplyr::summarize(habNear = sum(habNear))
ggplot() + geom_line(data = truthNear, aes(x=time,y=habNear))
```



Pull salinity and temperature time series
```{r}
bboxes <- get_boundary(load_box(dir = dir, file_bgm = file_bgm))
truthTemp <- load_nc_physics(dir = dir, file_nc = "neusDynEffort_Oct23_08d_.nc",
                             physic_variables = "Temp", aggregate_layers = FALSE, 
                             bboxes = bboxes)

truthSal <- load_nc_physics(dir = dir, file_nc = "neusDynEffort_Oct23_08d_.nc",
                             physic_variables = "salt", aggregate_layers = FALSE, 
                             bboxes = bboxes)

truthPhys <- merge(truthTemp, truthSal, by = c("polygon", "layer", "time"))
truthPhys <- truthPhys %>% dplyr::select(polygon, layer, time, atoutput.x, atoutput.y) %>%
                rename(temp = atoutput.x, 
                       sal = atoutput.y) %>%
                filter(polygon %in% c(5, 7:11, 19))

# Use Chl-a for primary production indicator?
truthChla <- load_nc_physics(dir = dir, file_nc = "neusDynEffort_Oct23_08d_.nc",
                             physic_variables = "Chl_a", aggregate_layers = TRUE, 
                             bboxes = bboxes)
truthChla <- truthChla %>% filter(polygon %in% c(5, 7:11, 19)) %>%
                group_by(time) %>%
                dplyr::summarize(PP = sum(atoutput)) %>%
                filter(!time %in% c(0,51))

#!!! need to figure out how to translate into mg Chla/m^3?

unique(truthPhys[, c("polygon", "layer")])

truthPhys <- truthPhys %>% mutate(density = swRho(salinity = sal, temperature = temp, 
                                                  pressure = 0, eos = "unesco"))

# get temp and salinity at surface
surfaceST <- truthPhys %>% filter(layer == 0) %>%
                group_by(time) %>%
                dplyr::summarize(SST = mean(temp),
                                 SSS = mean(sal))

# get temp and salinity at bottom
bottomST <- truthPhys %>% filter(layer != 4) %>%
              group_by(polygon, time) %>%
              filter(layer == max(layer)) %>%
              ungroup() %>%
              group_by(time) %>%
              dplyr::summarize(BT = mean(temp),
                               BS = mean(sal))

# get stratification (density difference) in Box 10
strat <- truthPhys %>% filter(polygon == 10, layer %in% c(0,1)) %>%
            group_by(time) %>%
            mutate(strat = diff(density, lag = 1)) %>%
            filter(layer == 0) %>%
            arrange(time)

plot(strat$time, strat$strat, type = "l")
```


Pull in catch by fishery to get recreational catch
```{r}
# poach code from load_catch()
file.catch <- file.path(dir, paste0(scenario, "CatchPerFishery.txt"))
recCatch <- read.table(file.catch, header = TRUE)

unique(recCatch$Fishery)

fgs <- fgs[fgs$IsTurnedOn > 0,]
fishedlookup <- fgs[fgs$isFished > 0,]
  
names(recCatch)[na.omit(match(fishedlookup$Code,names(recCatch)))] <- na.omit(fishedlookup$Name)
  
recCatch <- recCatch %>% filter(Fishery == "recfish") %>%
    tidyr::gather(species, catchbio, -Time, -Fishery)
  
out <- data.frame(species = recCatch$species,
                    agecl = NA,
                    polygon = NA,
                    layer = NA,
                    time = recCatch$Time,
                    atoutput = recCatch$catchbio)
  
out <- out[order(out$species,out$time,out$polygon,out$agecl),]

```

Use record of recreational effort instead
```{r}
file.catch <- file.path(dir, paste0(scenario, "Effort.txt"))
recEffort <- read.table(file.catch, header = TRUE)

matplot(recEffort$Time/365, recEffort[,-c(1,26)], type = "l")

recEffort <- recEffort %>% dplyr::select(Time, recfish) %>%
                mutate(time = Time/365) %>%
                rename(recParticip = recfish)
plot(recEffort$Time/365, recEffort$recParticip)
```

Create timeseries of categories for baleen whales and pinnipeds
```{r}
marmams <- truth$nums %>% dplyr::filter(species %in% c("Pinniped", "Whale_Baleen"), 
                                        polygon %in% c(5, 7:11, 19)) 

marmams <- marmams %>%
              group_by(species, time) %>% 
              dplyr::summarize(Num = sum(atoutput))
ggplot() + geom_line(data = marmams, aes(x=time,y=Num)) +
      facet_wrap(~species, scales = "free")

marmams <- marmams %>% pivot_wider(names_from = species, values_from = Num)

# modify code from ProcessData.Rmd
marmams$catHL <- ifelse(test = marmams$Pinniped < mean(marmams$Pinniped),#log(greySeals$Mean...2) < mean(log(greySeals$Mean...2)), 
                          yes = "Low", 
                          no = "High")
marmams$rwIorD <- NA
for(i in 1:(nrow(marmams)-1)){
  marmams$rwIorD[i+1] <- if(marmams$Whale_Baleen[i+1] < marmams$Whale_Baleen[i]){
                            "Decreasing"
                          } else {"Increasing"} # assumes no change = increasing
}

marmams$PS <- paste(marmams$catHL, marmams$rwIorD, sep = "")

marmams <- marmams %>% filter(!time %in% c(0, 51))
```

Lower trophic component indicators
```{r}
# Gelatinous Zooplankton
gzGB <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                     bps = bps, fgs = fgs, 
                     select_groups = c("Gelat_Zoo"),
                     select_variable = "N", bboxes = bboxes)
gzGB <- gzGB %>% filter(polygon %in% c(5, 7:11, 19))

gzGB <- gzGB %>% group_by(species, time) %>% 
          dplyr::summarize(GZ = sum(atoutput))
ggplot() + geom_line(data = gzGB, aes(x=time,y=GZ))

# Copepods and Micronekton
cmGB <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                     bps = bps, fgs = fgs, 
                     select_groups = c("Zoo", "MicroZoo"),
                     select_variable = "N", bboxes = bboxes)
cmGB <- cmGB %>% filter(polygon %in% c(5, 7:11, 19))

cmGB <- cmGB %>% group_by(time) %>% 
          dplyr::summarize(copepod = sum(atoutput))
ggplot() + geom_line(data = cmGB, aes(x=time,y=copepod))

# Benthos
benthGB <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                     bps = bps, fgs = fgs, 
                     select_groups = indBDNLookup[indBDNLookup$BNindexGroup == "benthos", "Name"],
                     select_variable = "N", bboxes = bboxes)
benthGB <- benthGB %>% filter(polygon %in% c(5, 7:11, 19))

benthGB <- benthGB %>% group_by(time) %>% 
          dplyr::summarize(benthos = sum(atoutput))
ggplot() + geom_line(data = benthGB, aes(x=time,y=benthos))

# Detritus & Bacteria
detBacGB <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                     bps = bps, fgs = fgs, 
                     select_groups = indBDNLookup[indBDNLookup$BNindexGroup == "detBac", "Name"],
                     select_variable = "N", bboxes = bboxes)
detBacGB <- detBacGB %>% filter(polygon %in% c(5, 7:11, 19))

detBacGB <- detBacGB %>% group_by(time) %>% 
          dplyr::summarize(detBac = sum(atoutput))
ggplot() + geom_line(data = detBacGB, aes(x=time,y=detBac))

# Mid-Atlantic Bight Groundfish
gfMABGB <- biomassTruth %>% filter(species %in% indBDNLookup[indBDNLookup$BNindexGroup == "gfMAB", "Name"]) %>%
            filter(polygon %in% c(5, 7:11, 19)) %>%
            group_by(time) %>% 
            dplyr::summarize(gfMAB = sum(atoutput))
ggplot() + geom_line(data = gfMABGB, aes(x=time,y=gfMAB))
```

Gather together for assessment model input
```{r}
neusHistoricData <- bottomST %>% full_join(surfaceST, by = "time") %>%
                      full_join(strat, by = "time") %>%
                      full_join(truthChla, by = "time") %>%
                      full_join(detBacGB, by = "time") %>%
                       full_join(gfMABGB, by = "time") %>%
                       full_join(benthGB, by = "time") %>%
                       full_join(cmGB, by = "time") %>%
                       full_join(gzGB, by = "time") %>%
                       full_join(commSF, by = "time") %>%
                       full_join(commPel, by = "time") %>%
                       full_join(commGF, by = "time") %>%
                       full_join(habDem, by = "time") %>%
                       full_join(truthNear, by = "time") %>%
                       full_join(habPel, by = "time") %>%
                       full_join(invertsGB, by = "time") %>%
                       full_join(groundGB, by = "time") %>%
                       full_join(forageGB, by = "time") %>%
                       full_join(marmams, by = "time") %>%
                       full_join(recEffort, by = "time") %>%
                       select(time, BT, BS, SST, SSS, strat, PP, detBac, 
                              gfMAB, benthos, copepod, GZ, 
                              commSF, commPel, commGF, habDem, habNear, habPel, 
                              inverts, ground, forage, PS, recParticip)

neusHistoricData <- neusHistoricData %>% filter(time != 0) %>%
                      filter(time <= 50)

# save(neusHistoricData, file = "C:/Users/rwildermuth/Dropbox/PhD_UMass/ATLANTIS/omNEUS/neusHistoricData.RData")

neusHistoricData %>% select( -c("time", "PS")) %>% cor(method = "spearman")
```

# Run data extraction on scenario outputs

Set up input for pseudo-data extraction and get the 'truth'
```{r}
# Bring in lookup of Atlantis codes and names for BDN node indices
indBDNLookup <- read.csv("C:/Users/rwildermuth/Dropbox/PhD_UMass/ATLANTIS/NeusGroups_modforusewNEUS1.0.csv", 
                         stringsAsFactors = FALSE)
indBDNLookup <- indBDNLookup %>% dplyr::select(Code, Name, Long.Name, BNindexGroup) %>%
                  filter(BNindexGroup != "")

# MSE scenario
scenarioMSEfolder <- "Oct23_08d"

# function args
scenario = "neusDynEffort_Oct23_08d_" # Output file prefix
dir = paste0("C:/Users/rwildermuth/Documents/AtlantisTesting/FishingScenarios/",
             scenarioMSEfolder)
file_fgs = "NeusGroups_modforusewNEUS1.0.csv"
file_bgm = "neus30_2006.bgm" # geography bgm for box definitions
select_groups = indBDNLookup$Name
                # c("Diatom", # the group 'Name's in the 'file_fgs' file
                #   "DinoFlag",
                #   "PicoPhytopl",
                #   "Lab_Det",
                #   "Ref_Det",
                #   "Pisciv_S_Fish",
                #   "Demersal_DC_Fish",
                #   "Macrobenth_Shallow",
                #   "Benthic_grazer",
                #   "Benthic_Carniv",
                #   "Deposit_Feeder",
                #   "Zoo",
                #   "MicroZoo",
                #   "Gelat_Zoo",
                #   "Pinniped",
                #   "Whale_Baleen",
                #   "Pisciv_D_Fish",
                #   "Pisciv_B_Fish",
                #   "Demersal_D_Fish",
                #   "Demersal_S_Fish",
                #   "Demersal_B_Fish",
                #   "Demersal_DC_Fish",
                #   "Demersal_O_Fish",
                #   "Demersal_F_Fish",
                #   "Shark_B",
                #   "Shark_D",
                #   "SkateRay",
                #   "Filter_Shallow",
                #   "Filter_Other",
                #   "Megazoobenthos",
                #   "Prawn",
                #   "Planktiv_L_Fish",
                #   "Planktiv_S_Fish",
                #   "Demersal_E_Fish",
                #   "Cephalopod",
                #   "Benthopel_Fish", 
                #   "Meiobenth")
# try shorter group list
# select_groups = c("Pinniped",
#                   "Whale_Baleen",
#                   "Pisciv_D_Fish",
#                   "Pisciv_B_Fish",
#                   "Demersal_D_Fish",
#                   "Demersal_S_Fish")
file_init = "inneus_2007.nc" # initial condition .nc file
file_biolprm = "at_biol_neus_Oct10B_Jason_FE.prm" # -b flag in the batch file
file_runprm = "Run_settings.xml" # needed for catch correction calculation, how to replace? -r flag in batch file
verbose = FALSE



# Use modified run_truth()
# truth <- run_truth(scenario = scenario,
#                    dir = dir,
#                    file_fgs = file_fgs,
#                    file_bgm = file_bgm,
#                    select_groups = select_groups,
#                    file_init = file_init,
#                    file_biolprm = file_biolprm,
#                    file_runprm = "NEUSv1",
#                    # saves to folder containing the Atlantis output
#                    save = TRUE)
load(paste0(dir, "/", scenario, "run_truth.RData"))
truth <- result
```


# Adding measurement error
Apply survey sampling OM functions to biomass truth
These methods follow S. Gaichas and C. Stawitz here: https://sgaichas.github.io/poseidon-dev/NEUSStandardSurveyTest.html and https://sgaichas.github.io/poseidon-dev/StandardSurveyTest.html
```{r}
# species groupings for different exposure to the survey
# RW: edited for returning vert groups listed in 'indBDNLookup'
nontrawl <- c("Shark_D", "Pinniped", "Whale_Baleen")
pelagics <- c("Planktiv_L_Fish", "Planktiv_S_Fish", "Benthopel_Fish", "Pisciv_S_Fish")
demersals <- c("Pisciv_D_Fish", "Demersal_D_Fish","Demersal_E_Fish", 
                 "Demersal_S_Fish","Demersal_B_Fish","Demersal_DC_Fish",
                 "Demersal_O_Fish","Demersal_F_Fish",
                 "Shark_B", "SkateRay")
selflats <- c("Pisciv_B_Fish")
survspp <- c(nontrawl, pelagics, demersals, selflats)

# Use hardcoded fall sampling frame for NEUS 1.0 in trunk here
annualfall <- seq(4,202,4)


#   define bottom trawl mixed efficiency
ef.nt <- 0.01 # for large pelagics, reef dwellers, others not in trawlable habitat
ef.pl <- 0.1  # for pelagics
ef.dm <- 0.7  # for demersals
ef.fl <- 1.1  # for selected flatfish

# bottom trawl survey efficiency specification by species group
effnontrawl <- data.frame(species=nontrawl, efficiency=rep(ef.nt,length(nontrawl)))
effpelagics <- data.frame(species=pelagics, efficiency=rep(ef.pl,length(pelagics)))
effdemersals <- data.frame(species=demersals, efficiency=rep(ef.dm,length(demersals)))
effselflats <- data.frame(species=selflats, efficiency=rep(ef.fl,length(selflats)))

efficmix <- bind_rows(effnontrawl, effpelagics, effdemersals, effselflats)

#   mixed selectivity (using 10 agecl for all species)
#     flat=1 for large pelagics, reef dwellers, others not in trawlable habitat
#     sigmoid 0 to 1 with 0.5 inflection at agecl 3 for pelagics, reaching 1 at agecl 5, flat top
#     sigmoid 0 to 1 with 0.5 inflection at agecl 5 for most demersals and flatfish, reaching 1 at agecl 7, flat top
#     dome shaped 0 to 1 at agecl 6&7 for selected demersals, falling off to 0.7 by agecl 10

sigmoid <- function(a,b,x) {
  1 / (1 + exp(-a-b*x))
}

# survey selectivity specification by species group
selnontrawl <- data.frame(species=rep(nontrawl, each=10),
                          agecl=rep(c(1:10),length(nontrawl)),
                          selex=rep(1.0,length(nontrawl)*10))
selpelagics <- data.frame(species=rep(pelagics, each=10),
                          agecl=rep(c(1:10),length(pelagics)),
                          selex=sigmoid(5,1,seq(-10,10,length.out=10)))
seldemersals <- data.frame(species=rep(demersals, each=10),
                          agecl=rep(c(1:10),length(demersals)),
                          selex=sigmoid(1,1,seq(-10,10,length.out=10)))
selselflats <- data.frame(species=rep(selflats, each=10),
                          agecl=rep(c(1:10),length(selflats)),
                          selex=sigmoid(1,1,seq(-10,10,length.out=10)))

# same selectivity for selflats and demersals specified above
# visualze selectivity curves for each group
par(mfrow=c(2,2))
par(mar=c(4,4,1,1))
plot(selnontrawl$agecl, selnontrawl$selex)
plot(selpelagics$agecl, selpelagics$selex)
plot(seldemersals$agecl, seldemersals$selex)
plot(selselflats$agecl, selselflats$selex)

selexmix <- bind_rows(selnontrawl, selpelagics, seldemersals, selselflats)

# use this constant 0 cv for testing
#surv_cv_0 <- data.frame(species=survspp, cv=rep(0.0,length(survspp)))

#   define bottom trawl survey cv by group
cv.nt <- 1.0 # for large pelagics, reef dwellers, others not in trawlable habitat
cv.pl <- 0.5  # for pelagics
cv.dm <- 0.3  # for demersals
cv.fl <- 0.3  # for selected flatfish

# specify cv by species groups
surv_cv_nontrawl <- data.frame(species=nontrawl, cv=rep(cv.nt,length(nontrawl)))
surv_cv_pelagics <- data.frame(species=pelagics, cv=rep(cv.pl,length(pelagics)))
surv_cv_demersals <- data.frame(species=demersals, cv=rep(cv.dm,length(demersals)))
surv_cv_selflats <- data.frame(species=selflats, cv=rep(cv.fl,length(selflats)))

surv_cv_mix <- bind_rows(surv_cv_nontrawl, surv_cv_pelagics, surv_cv_demersals, surv_cv_selflats)

# use biomasses from 'truth' via run_truth() to sample and add survey error
survey_testBstd <- create_survey(dat = biomassTruth,
                                 time = annualfall,
                                 species = survspp,
                                 boxes = c(5,7:11,19), # Georges Bank boxes
                                 effic = efficmix,
                                 selex = selexmix)

# call sample_survey_biomass with a bunch of 1s for weight at age
# in the code it multiplies atoutput by wtatage so this allows us to use
# biomass directly
wtage <- data.frame(species=rep(survspp, each=10),
                    agecl=rep(c(1:10),length(survspp)),
                    wtAtAge=rep(1.0,length(survspp)*10))

stdsurveyB_frombio <- sample_survey_biomass(survey_testBstd, surv_cv_mix, wtage)

# Want numbers for pinnipeds and baleen whales though
```