---
title: "Get Atlantis pseudo-data"
author: "Robert Wildermuth"
date: "10/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load atlantisom package and replacement functions
```{r}
library(atlantisom)
library(tidyverse)

source("C:/Users/rwildermuth/Dropbox/PhD_UMass/ATLANTIS/omNEUS/load_neus_v1_runprm.R")
source("C:/Users/rwildermuth/Dropbox/PhD_UMass/ATLANTIS/omNEUS/run_truth.R")
```

Set up input for pseudo-data extraction and get the 'truth'
```{r}
# Bring in lookup of Atlantis codes and names for BDN node indices
indBDNLookup <- read.csv("C:/Users/rwildermuth/Dropbox/PhD_UMass/ATLANTIS/NeusGroups_modforusewNEUS1.0.csv", 
                         stringsAsFactors = FALSE)
indBDNLookup <- indBDNLookup %>% dplyr::select(Code, Name, Long.Name, BNindexGroup) %>%
                  filter(BNindexGroup != "")

# function args
scenario = "neusDynEffort_Oct23_08d_"
dir = "//storage1.smast.umassd.edu/lab_fay/rwildermuth/ATLANTIS/scenarios/Oct23_08d"
file_fgs = "NeusGroups_modforusewNEUS1.0.csv"
file_bgm = "neus30_2006.bgm" # geography bgm for box definitions
select_groups = indBDNLookup$Name
                # c("Diatom", # the group 'Name's in the 'file_fgs' file
                #   "DinoFlag",
                #   "PicoPhytopl",
                #   "Lab_Det",
                #   "Ref_Det",
                #   "Pisciv_S_Fish",
                #   "Demersal_DC_Fish",
                #   "Macrobenth_Shallow",
                #   "Benthic_grazer",
                #   "Benthic_Carniv",
                #   "Deposit_Feeder",
                #   "Zoo",
                #   "MicroZoo",
                #   "Gelat_Zoo",
                #   "Pinniped",
                #   "Whale_Baleen",
                #   "Pisciv_D_Fish",
                #   "Pisciv_B_Fish",
                #   "Demersal_D_Fish",
                #   "Demersal_S_Fish",
                #   "Demersal_B_Fish",
                #   "Demersal_DC_Fish",
                #   "Demersal_O_Fish",
                #   "Demersal_F_Fish",
                #   "Shark_B",
                #   "Shark_D",
                #   "SkateRay",
                #   "Filter_Shallow",
                #   "Filter_Other",
                #   "Megazoobenthos",
                #   "Prawn",
                #   "Planktiv_L_Fish",
                #   "Planktiv_S_Fish",
                #   "Demersal_E_Fish",
                #   "Cephalopod",
                #   "Benthopel_Fish", 
                #   "Meiobenth")
# try shorter group list
select_groups = c("Pinniped",
                  "Whale_Baleen",
                  "Pisciv_D_Fish",
                  "Pisciv_B_Fish",
                  "Demersal_D_Fish",
                  "Demersal_S_Fish")
file_init = "inneus_2007.nc" # initial condition .nc file
file_biolprm = "at_biol_neus_Oct10B_Jason_FE.prm" # -b flag in the batch file
file_runprm = "Run_settings.xml" # needed for catch correction calculation, how to replace? -r flag in batch file
verbose = FALSE



# Use modified run_truth()
# truth <- run_truth(scenario = scenario,
#                    dir = dir,
#                    file_fgs = file_fgs,
#                    file_bgm = file_bgm,
#                    select_groups = select_groups,
#                    file_init = file_init,
#                    file_biolprm = file_biolprm,
#                    file_runprm = "NEUSv1",
#                    # saves to folder containing the Atlantis output
#                    save = TRUE)
load(paste0(dir, "/", scenario, "run_truth.RData"))
truth <- result
```

Investigate differences in catch from .txt file and from spatially-explicit .nc file
```{r}
# get 'catch_all' in terms of group names
fxnlGroups <- load_fgs(dir, file_fgs = file_fgs)

codeNameMatch <- merge(truth$catch_all, fxnlGroups[, c("Code", "Name")], by.x = "species", by.y = "Code")

truth$catch_all$species <- codeNameMatch$Name

# subset to groups in 'select_groups'
truth$catch_all <- truth$catch_all %>% dplyr::filter(species %in% select_groups)

compare_catchB <-ggplot() +
  geom_line(data=truth$bio_catch, aes(x=time,y=atoutput, #color="catch atlantisom"
                                      ), 
            alpha = 10/10) +
  geom_point(data=truth$catch_all, aes(x=time,y=atoutput, #color="txt output catch bio"
                                       ), # has all spp in Atlantis codes, not Names
             alpha = 1/10) + 
  theme_minimal() +
  theme(legend.position = "top") 
  #labs(colour=scenario.name)

# compare_catchB + 
#   facet_wrap(~species, ncol=3, nrow = 2, scales="free")

# need to sum among 'bio_catch' values between time intervals in 'catch_all'
truth$bio_catch$timeAgg <- 0

for(i in 2:nrow(truth$catch_all)){
  for(j in 1:nrow(truth$bio_catch)){
    if(truth$bio_catch$time[j] > truth$catch_all$time[i-1] & 
       truth$bio_catch$time[j] <= truth$catch_all$time[i]){
      truth$bio_catch$timeAgg[j] <- truth$catch_all$time[i]
    }
  }
}

aggBioCatch <- truth$bio_catch %>% group_by(species, timeAgg) %>%
            dplyr::summarize(catchAgg = sum(atoutput),
                             n = n())

check <- merge(truth$catch_all, aggBioCatch,
               by.x = c("species", "time"), by.y = c("species", "timeAgg"))
check$check <- with(check, atoutput / catchAgg)

check %>% group_by(time) %>%
  dplyr::summarize(minScale = min(check),
                   maxScale = max(check))
check %>% pivot_wider(id_cols = time, names_from = species, values_from = check)
```

Get the catches by species for Georges Bank
```{r}
# Subset to Georges Bank boxes and apply biomass conversion
bio_catchGB <- calc_biomass_age(nums = truth$catch,
                                resn = truth$resn, structn = truth$structn, biolprm = truth$biol)
bio_catchGB <- bio_catchGB %>% filter(polygon %in% c(5, 7:11, 19)) %>%
                  # Divide box 5 values in half 
                  mutate(atoutput = case_when(polygon == 5 ~ atoutput/2,
                                              polygon != 5 ~ atoutput)) 
bio_catchGB <- aggregate(atoutput ~ species + time,
                         data = bio_catchGB, sum)

# compare_catchB + 
#   geom_line(data=bio_catchGB, aes(x=time,y=atoutput, color="blue"), 
#             alpha = 10/10) +
#   facet_wrap(~species, ncol=3, nrow = 2, scales="free")

# need to sum among 'bio_catchGB' values between time intervals in 'catch_all'
bio_catchGB$timeAgg <- 0

for(i in 2:nrow(truth$catch_all)){
  for(j in 1:nrow(bio_catchGB)){
    if(bio_catchGB$time[j] > truth$catch_all$time[i-1] & 
       bio_catchGB$time[j] <= truth$catch_all$time[i]){
      bio_catchGB$timeAgg[j] <- truth$catch_all$time[i]
    }
  }
}

aggBioCatchGB <- bio_catchGB %>% group_by(species, timeAgg) %>%
            dplyr::summarize(catchAgg = sum(atoutput),
                             n = n())

# Find proportion of catch biomass in Georges Bank by species
aggBioCatchGB <- merge(aggBioCatchGB, aggBioCatch, by = c("species", "timeAgg"))
aggBioCatchGB$propGB <- with(aggBioCatchGB, catchAgg.x/catchAgg.y)

# multiply .txt catch by Georges Bank proportions and create pseudo-data time series
catchGB <- merge(truth$catch_all, aggBioCatchGB, 
                 by.x = c("species", "time"), by.y = c("species", "timeAgg"))
# remove initial year and unneeded columns
catchGB <- catchGB %>% filter(time != 0) %>%
              dplyr::select(species, time, atoutput, propGB) %>%
              mutate(catch = atoutput * propGB)

# compare_catchB + 
#   geom_line(data=catchGB, aes(x=time,y=catch, color="GB catch"), 
#             alpha = 10/10) +
#   facet_wrap(~species, ncol=3, nrow = 2, scales="free")
```

Explore variation in data indices for habitat calculations
```{r}
test5 <- aggregate(atoutput ~ species + time + polygon,
                         data = truth$nums, sum)
test5 %>% filter(species == "Demersal_D_Fish")

ggplot() +
  geom_line(data=test5, aes(x=time,y=atoutput, color=polygon), 
            alpha = 10/10) +
  facet_wrap(~species, ncol=3, nrow = 2, scales="free")

test5 %>% filter(#species == "Demersal_D_Fish", 
                 polygon %in% c(5, 7:11, 19)) %>%
  ggplot() +
  geom_line(aes(x=time,y=atoutput, color=polygon), 
            alpha = 10/10) +
  facet_wrap(~species, ncol=3, nrow = 3, scales="free")

# maybe use condition factor?
condition <- merge(truth$resn, truth$structn, by = c("species", "agecl", "polygon", "layer", "time"))
condition$condition <- condition$atoutput.x/condition$atoutput.y

test6 <- condition %>% filter(condition < 2.65)
test6 <- condition %>% filter(condition > 2.65)
unique(unique(test6[,-c(6:8)])[, c("species", "agecl")])
dim(condition); dim(test6)
# need to select by mature age classes
matOgive <- truth$biolprm$maturityogive
matOgive <- merge(matOgive, fxnlGroups[, c("Code", "Name")], by.x = "code", by.y = "Code")
names(matOgive)[which(names(matOgive) == " agecl10")] <- "agecl10"
matOgive <- matOgive %>% dplyr::select("Name", paste0("agecl", 1:10)) %>%
              pivot_longer(cols = starts_with("agecl"), names_to = "agecl",
                           names_prefix = "agecl", names_ptypes = numeric(),
                           values_to = "propMat_fctr") %>%
              mutate(agecl = as.numeric(agecl),
                     propMat = as.numeric(as.character(propMat_fctr)))

#Calculate habitat as the number of mature indivs * their condition ratio
numMat <- merge(truth$nums, matOgive, by.x = c("species", "agecl"), by.y = c("Name", "agecl"))
numMat <- numMat %>% dplyr::select(species, agecl, polygon, layer, time, atoutput, propMat) %>%
            mutate(numMat = atoutput * propMat)
numMat <- merge(numMat, condition, by = c("species", "agecl", "polygon", "layer", "time"))

# need separate dataset for Nearshore Habitat
# doesn't work b/c no age groups -> no maturity ogive
numMatNear <- numMat %>% filter(species %in% c("Filter_Other",
                                               "Deposit_Feeder",
                                               "Meiobenth"))
  
numMat <- numMat %>% mutate(condIndex = numMat * condition)

numMat <- numMat %>% group_by(species, time) %>%
            dplyr::select(species, agecl, polygon, layer, time, condIndex) %>%
            dplyr::summarize(condIndex = sum(condIndex))

# ggplot() + 
#   geom_line(data=numMat, aes(x=time,y=condIndex), 
#             alpha = 10/10) +
#   facet_wrap(~species, ncol=3, nrow = 2, scales="free")

# aggregate by focal group similar to BDN
# Seafloor and Demersal Habitat
habDem <- numMat %>% filter(species %in% indBDNLookup[indBDNLookup$BNindexGroup == "groundfish",
                                                      "Name"])
habDem <- habDem %>% group_by(time) %>%
            dplyr::summarize(condIndex = sum(condIndex))
plot(habDem$time, habDem$condIndex, type = "l")

# Pelagic Habitat
habPel <- numMat %>% filter(species %in% indBDNLookup[indBDNLookup$BNindexGroup == "forage",
                                                      "Name"])
habPel <- habPel %>% group_by(time) %>%
            dplyr::summarize(condIndex = sum(condIndex))
plot(habPel$time, habPel$condIndex, type = "l")

# Nearshore Habitat
# do similar, but only for  lower trophic benthic groups for half of Box 5
habNear <-  numMatNear %>% filter(polygon == 5) %>%
              mutate(condIndex = numMat/2 * condition) %>% 
              group_by(species, time) %>%
              dplyr::select(species, agecl, polygon, layer, time, condIndex) %>%
              dplyr::summarize(condIndex = sum(condIndex))
habNear <- habNear %>% group_by(time) %>%
            dplyr::summarize(condIndex = sum(condIndex))
plot(habNear$time, habNear$condIndex, type = "l")
```



Pull salinity and temperature time series
```{r}
bboxes <- get_boundary(load_box(dir = dir, file_bgm = file_bgm))
truthTemp <- load_nc_physics(dir = dir, file_nc = "neusDynEffort_Oct23_08d_.nc",
                             physic_variables = "Temp", aggregate_layers = FALSE, 
                             bboxes = bboxes)

truthSal <- load_nc_physics(dir = dir, file_nc = "neusDynEffort_Oct23_08d_.nc",
                             physic_variables = "salt", aggregate_layers = FALSE, 
                             bboxes = bboxes)

truthPhys <- merge(truthTemp, truthSal, by = c("polygon", "layer", "time"))
truthPhys <- truthPhys %>% dplyr::select(polygon, layer, time, atoutput.x, atoutput.y) %>%
                rename(temp = atoutput.x, 
                       sal = atoutput.y) %>%
                filter(polygon %in% c(5, 7:11, 19))

# maybe use Chl-a as nearshore habitat indicator?
truthChla <- load_nc_physics(dir = dir, file_nc = "neusDynEffort_Oct23_08d_.nc",
                             physic_variables = "Chl_a", aggregate_layers = TRUE, 
                             bboxes = bboxes)
```

Try to get biomass of bio pools for nearshore habitat and lower trophic groups
```{r}
bps <- load_bps(dir = dir, fgs = file_fgs, file_init = file_init)
fgs <- load_fgs(dir = dir, file_fgs = file_fgs)
invertPools <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                     bps = bps, fgs = fgs, 
                     select_groups = c("Filter_Other",
                                       "Deposit_Feeder",
                                       "Meiobenth"),
                     select_variable = "N", bboxes = bboxes)
#truthNear <- truthNear %>% filter(polygon == 5)

test2 <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                        bps = bps, fgs = fgs, 
                        select_groups = c("Benthopel_Fish"),
                        select_variable = "N", bboxes = bboxes)
test3 <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                        bps = bps, fgs = fgs, 
                        select_groups = c("Benthopel_Fish"),
                        select_variable = "ResN", bboxes = bboxes)
test4 <- load_nc(dir = dir, file_nc = paste0(scenario, ".nc"),
                        bps = bps, fgs = fgs, 
                        select_groups = c("Benthopel_Fish"),
                        select_variable = "StructN", bboxes = bboxes)
test2 %>% filter(polygon == 5, time == 0, layer == 0) # not the sum of structN and resN
test3 %>% filter(polygon == 5, time == 0, layer == 0)
test4 %>% filter(polygon == 5, time == 0, layer == 0)
```

Calculate wet weight of biomass pools using conversion in Atlantis manual, pg 151: weight_g = (1 + 2.65) * strutural N
```{r}
# Ratio of reserve to structural N for NEUS is 2.65
invertPools$atoutput <- invertPools$atoutput * (1 + 2.65)

# convert to weight in tonnes?
invertPools$test1 <- invertPools$atoutput / 1e6
```

# Adding measurement error
Apply survey sampling OM functions to biomass truth
These methods follow S. Gaichas and C. Stawitz here: https://sgaichas.github.io/poseidon-dev/NEUSStandardSurveyTest.html and https://sgaichas.github.io/poseidon-dev/StandardSurveyTest.html
```{r}
# species groupings for different exposure to the survey
# RW: edited for returning vert groups listed in 'indBDNLookup'
nontrawl <- c("Shark_D", "Pinniped", "Whale_Baleen")
pelagics <- c("Planktiv_L_Fish", "Planktiv_S_Fish", "Benthopel_Fish", "Pisciv_S_Fish")
demersals <- c("Pisciv_D_Fish", "Demersal_D_Fish","Demersal_E_Fish", 
                 "Demersal_S_Fish","Demersal_B_Fish","Demersal_DC_Fish",
                 "Demersal_O_Fish","Demersal_F_Fish",
                 "Shark_B", "SkateRay")
selflats <- c("Pisciv_B_Fish")
survspp <- c(nontrawl, pelagics, demersals, selflats)

# Use hardcoded fall sampling frame for NEUS 1.0 in trunk here
annualfall <- seq(4,202,4)


#   define bottom trawl mixed efficiency
ef.nt <- 0.01 # for large pelagics, reef dwellers, others not in trawlable habitat
ef.pl <- 0.1  # for pelagics
ef.dm <- 0.7  # for demersals
ef.fl <- 1.1  # for selected flatfish

# bottom trawl survey efficiency specification by species group
effnontrawl <- data.frame(species=nontrawl, efficiency=rep(ef.nt,length(nontrawl)))
effpelagics <- data.frame(species=pelagics, efficiency=rep(ef.pl,length(pelagics)))
effdemersals <- data.frame(species=demersals, efficiency=rep(ef.dm,length(demersals)))
effselflats <- data.frame(species=selflats, efficiency=rep(ef.fl,length(selflats)))

efficmix <- bind_rows(effnontrawl, effpelagics, effdemersals, effselflats)

#   mixed selectivity (using 10 agecl for all species)
#     flat=1 for large pelagics, reef dwellers, others not in trawlable habitat
#     sigmoid 0 to 1 with 0.5 inflection at agecl 3 for pelagics, reaching 1 at agecl 5, flat top
#     sigmoid 0 to 1 with 0.5 inflection at agecl 5 for most demersals and flatfish, reaching 1 at agecl 7, flat top
#     dome shaped 0 to 1 at agecl 6&7 for selected demersals, falling off to 0.7 by agecl 10

sigmoid <- function(a,b,x) {
  1 / (1 + exp(-a-b*x))
}

# survey selectivity specification by species group
selnontrawl <- data.frame(species=rep(nontrawl, each=10),
                          agecl=rep(c(1:10),length(nontrawl)),
                          selex=rep(1.0,length(nontrawl)*10))
selpelagics <- data.frame(species=rep(pelagics, each=10),
                          agecl=rep(c(1:10),length(pelagics)),
                          selex=sigmoid(5,1,seq(-10,10,length.out=10)))
seldemersals <- data.frame(species=rep(demersals, each=10),
                          agecl=rep(c(1:10),length(demersals)),
                          selex=sigmoid(1,1,seq(-10,10,length.out=10)))
selselflats <- data.frame(species=rep(selflats, each=10),
                          agecl=rep(c(1:10),length(selflats)),
                          selex=sigmoid(1,1,seq(-10,10,length.out=10)))

# same selectivity for selflats and demersals specified above
# visualze selectivity curves for each group
par(mfrow=c(2,2))
par(mar=c(4,4,1,1))
plot(selnontrawl$agecl, selnontrawl$selex)
plot(selpelagics$agecl, selpelagics$selex)
plot(seldemersals$agecl, seldemersals$selex)
plot(selselflats$agecl, selselflats$selex)

selexmix <- bind_rows(selnontrawl, selpelagics, seldemersals, selselflats)

# use this constant 0 cv for testing
#surv_cv_0 <- data.frame(species=survspp, cv=rep(0.0,length(survspp)))

#   define bottom trawl survey cv by group
cv.nt <- 1.0 # for large pelagics, reef dwellers, others not in trawlable habitat
cv.pl <- 0.5  # for pelagics
cv.dm <- 0.3  # for demersals
cv.fl <- 0.3  # for selected flatfish

# specify cv by species groups
surv_cv_nontrawl <- data.frame(species=nontrawl, cv=rep(cv.nt,length(nontrawl)))
surv_cv_pelagics <- data.frame(species=pelagics, cv=rep(cv.pl,length(pelagics)))
surv_cv_demersals <- data.frame(species=demersals, cv=rep(cv.dm,length(demersals)))
surv_cv_selflats <- data.frame(species=selflats, cv=rep(cv.fl,length(selflats)))

surv_cv_mix <- bind_rows(surv_cv_nontrawl, surv_cv_pelagics, surv_cv_demersals, surv_cv_selflats)

# use biomasses from 'truth' via run_truth() to sample and add survey error
biomassTruth <- calc_biomass_age(nums = truth$nums,
                                 resn = truth$resn, structn = truth$structn, biolprm = truth$biol)

survey_testBstd <- create_survey(dat = biomassTruth,
                                 time = annualfall,
                                 species = survspp,
                                 boxes = c(5,7:11,19), # Georges Bank boxes
                                 effic = efficmix,
                                 selex = selexmix)

# call sample_survey_biomass with a bunch of 1s for weight at age
# in the code it multiplies atoutput by wtatage so this allows us to use
# biomass directly
wtage <- data.frame(species=rep(survspp, each=10),
                    agecl=rep(c(1:10),length(survspp)),
                    wtAtAge=rep(1.0,length(survspp)*10))

stdsurveyB_frombio <- sample_survey_biomass(survey_testBstd, surv_cv_mix, wtage)

# Want numbers for pinnipeds and baleen whales though
```